Investment in reproduction by 14 iteroparous perennials and its coordination with other life-history and functional traits

### 2017-12-06 ms/RA/Wenk-RA-SI.Rnw
Updating figures for RA and adding SuppMatt
- added lat & lon to site file by converting from UTM coordinates (closes #31)
- added maps of filed sites
- reformatted suppmat style (it broke)

\title{Coordinated shifts in allocation among reproductive tissues across 14 coexisting plant species}
\runninghead{S\lowercase{hifts in allocation among reproductive tissues}}

\author{E. H. Wenk\textsuperscript{1,\textasteriskcentered}, K. Abramowicz\textsuperscript{2}, M. Westoby\textsuperscript{1}, D.S. Falster\textsuperscript{1} }
\affiliation{\textsuperscript{1} Biological Sciences, Macquarie University NSW 2109, Australia \\
\textsuperscript{2} Department of Mathematics and Mathematical Statistics, Ume{\aa} University, 90187 Ume{\aa}, Sweden \\
\textsuperscript{\textasteriskcentered} Correspondence author. E-mail: \email{ehwenk@gmail.com}
}

\usepackage[authoryear,sectionbib,sort]{natbib}
\bibliographystyle{amnat2}

@@

flowering_parts <- read.csv("Sup_Table_flowering_parts.csv", stringsAsFactors=FALSE, check.names=FALSE)
flowering_parts$Method <- clean_headers(flowering_parts$Method)
flowering_parts$Part <- firstup(flowering_parts$Part)
flowering_parts$Description <- firstup(flowering_parts$Description)

print_table_species <- function(species, data) {
  data <- data[data$Species == species, -c(1)]
  print(xtable(data,
            hline.after=c(1),
            align='p{0.1cm}p{4.5cm}p{6cm}p{2cm}p{1cm}p{1cm}',
            label=sprintf("tab:parts_%s", gsub(" ", "_", species)),
            caption=sprintf("Table of parts for \\emph{%s}.", species)),
      sanitize.text.function=I,
      , table.placement = "h"
      , caption.placement = "top"
      , include.rownames = FALSE
      , include.colnames = TRUE
      , size = "small"
      , tabular.environment = 'longtable'
      , floating = FALSE)
}

print_table_metadata <- function(path, align = NULL) {

  data <-  read.csv(path, stringsAsFactors=FALSE, check.names=FALSE)
  file <- gsub("_", "\\_", basename(path), fixed = TRUE)

  label <- sprintf("tab:%s_meta", strsplit(basename(path), "_")[[1]][1])

  print(xtable(data,
            align=align,
            hline.after=c(1),
            label= label,
            caption=
              sprintf("Description of variables within the file \\texttt{data/%s}. These definitions can also be found within the file \\texttt{data/%s}.",
              gsub("\\_meta", "", file, fixed = TRUE), file)),
      , table.placement = "h"
      , caption.placement = "top"
      , include.rownames = FALSE
      , include.colnames = TRUE
      , size = "small"
      , tabular.environment = 'longtable'
      , floating = FALSE)
}
@

@@

<<echo=FALSE, results='asis', warning=FALSE>>=

make_table_species_values_for_allocation_seedsize_table <- function(file) {
  data <- select(file,species,scaled_seed_count,scaled_ovule_count,
                 scaled_pollen_attract_costs,choosiness,prop_prepollen_success, prop_prepollen_discarded,
                 prop_postpollen_success,prop_postpollen_discarded, prop_pollen_attract_vs_success,prop_provisioning_vs_success)
  data$species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
  data
}

TableS15 <- make_table_species_values_for_allocation_seedsize_table(SummarySpp[["mean"]])

names(TableS15) <- c("species","seed count","ovule count","pollen-attraction costs","choosi- ness","success","discarded","success","discarded","pollen-attraction","provi- sioning")

for (i in 2:11) {
TableS15[,i] <- format(TableS15[,i],digits=3, nsmall=0)
}

TableS15$species  <- paste("\\textit{",unique(TableS15$species),"}", sep="")
@

\begin{table}[h]
\centering
\caption{Species values for data plotted in Figure 2: shifts in reproductive tissue allocation with seed size.  Counts and costs are per unit leaf area of the plant. The bottom line indicates the corresponding figure of the main text where the data are presented. Data for reproductive costs (Figure 2, panel a), Seed-size, pollen-attraction costs, and provisioning costs (Figure 2, panel f) are presented in Table 1 in the main text and are not included here.}
\label{tab:species}
{\footnotesize
\begin{tabular}{p{3cm}|p{1cm}p{1cm}|p{1cm}p{1cm}|p{1cm}p{1cm}|p{1cm}p{1cm}|p{1.5cm}p{1cm}}
\hline
& \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{Proportion} & \multicolumn{2}{c|}{Proportion}& \multicolumn{2}{c}{Proportion} \\
& \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{pollen-attraction} & \multicolumn{2}{c|}{provisioning}& \multicolumn{2}{c}{success} \\
& \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{} & \multicolumn{2}{c|}{investment to} & \multicolumn{2}{c|}{investment to}& \multicolumn{2}{c}{investment to} \\
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS15)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
cat("Figure reference & \\multicolumn{2}{c|}{Fig. 2, panel a} & \\multicolumn{2}{c|}{Fig. 2, panel b} & \\multicolumn{2}{c|}{Fig. 2, panel c} & \\multicolumn{2}{c|}{Fig. 2, panel d}  & \\multicolumn{2}{c}{Fig. 2, panel e}\\\\
\\hline")
@
\end{tabular}
}
\end{table}

\clearpage
<<echo=FALSE, results='asis', warning=FALSE>>=
make_table_RA_shifts_with_age <- function(SummaryInd) {
  xvar <- "repro_inv"
  yvar <- "accessory_costs"
  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
  accessory_vs_RE <- dplyr::select(fit$groupsummary,group,n,r2,pval)

  xvar <- "total_weight_0"
  yvar <- "accessory_costs"
  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
  accessory_vs_size <- dplyr::select(fit$groupsummary,group,n,r2,pval)

  xvar <- "age"
  yvar <- "accessory_costs"
  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy")
  accessory_vs_age <- dplyr::select(fit$groupsummary,group,n,r2,pval)

  TableS16 <- merge(accessory_vs_RE,accessory_vs_size,by="group")
  TableS16 <- merge(TableS16,accessory_vs_age,by="group")

  names(TableS16) <- c("Species","n","r$^2$","p","n","r$^2$","p","n","r$^2$","p")

  Species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
  TableS16$Species <-  paste("\\textit{",Species,"}", sep="")

  TableS16
}

TableS16 <- make_table_RA_shifts_with_age(SummaryInd)

for(i in c(2,3,5,6,8,9)){
  TableS16[,i] <- format_r2(TableS16[,i])
}
for(i in c(4,7,10)){
  TableS16[,i] <- format_p(TableS16[,i])
}
@

\begin{table}[H]
\centering
\caption{Testing for shifts in accessory costs with in age, plant size, or reproductive effort. Shifts in accessory costs with these variables is suggested as one possible explanation of increasing reproductive investment in larger, older plants, but such a trend did not exist in these data.}
\label{tab:access_vs_age}
\begin{tabular}{p{4cm}|x{.75cm}x{1cm}x{1.25cm}|x{.75cm}x{1cm}p{1.25cm}|x{.75cm}x{1cm}p{1.25cm}}
\hline
& \multicolumn{3}{c|}{Accessory costs} & \multicolumn{3}{c|}{Accessory costs}& \multicolumn{3}{c}{Accessory costs} \\
& \multicolumn{3}{c|}{vs. RE} & \multicolumn{3}{c|}{vs. plant mass}& \multicolumn{3}{c}{vs. age} \\
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS16)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

<<echo=FALSE, warning=FALSE>>=

make_table_propagule_invest_vs_all_repropro_inv <- function(SummaryInd) {
  mod_propagule_inv_all <- sma(repro_inv~propagule_inv,data=SummaryInd,log="xy",method="SMA")
  mod_flower_inv_all <- sma(repro_inv~flower_inv,data=SummaryInd,log="xy",method="SMA")

  yvar <- "repro_inv"
  xvar <- "propagule_inv"
  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA", log="xy",slope.test=mod_propagule_inv_all$groupsummary["Slope"][[1]],elev.test=mod_propagule_inv_all$coef[[1]][1,1])
  results <- fit$groupsummary
  acc_slopes <- dplyr::select(results,group,n,r2,pval)
  names(acc_slopes) <- c("Species","n_propagule","r2_propagule","p_propagule")

  yvar <- "repro_inv"
  xvar <- "flower_inv"
  data <- subset(SummaryInd,SummaryInd[[xvar]]>0&SummaryInd[[yvar]]>0)

  fit <- sma(data[[yvar]] ~ data[[xvar]]*data[["species"]], method="SMA",  log="xy",slope.test=mod_flower_inv_all$groupsummary["Slope"][[1]],elev.test=mod_flower_inv_all$coef[[1]][1,1])
  results <- fit$groupsummary
  acc_slopes2 <- dplyr::select(results,group,n,r2,pval)
  names(acc_slopes2) <- c("Species","n_flower","r2_flower","p_flower")
  acc_slopes <- dplyr::left_join(acc_slopes, acc_slopes2, by ="Species")
  names(acc_slopes) <- c("Species","n","r$^2$","p", "n","r$^2$","p")
  Species <- c("Banksia ericifolia","Boronia ledifolia","Conospermum ericifolium","Epacris microphylla", "Grevillea buxifolia","Grevillea speciosa","Hakea teretifolia", "Hemigenia purpurea","Leucopogon esquamatus","Persoonia lanceolata", "Petrophile pulchella", "Phyllota phylicoides", "Pimelea linifolia", "Pultenaea tuberculata")
  acc_slopes$Species <-  paste("\\textit{",Species,"}", sep="")

  acc_slopes
}

TableS17 <- make_table_propagule_invest_vs_all_repropro_inv(SummaryInd)

for(i in c(2,3,5,6)){
  TableS17[,i] <- format_r2(TableS17[,i])
}
for(i in c(4,7)){
  TableS17[,i] <- format_p(TableS17[,i])
}
@

\begin{table}[H]
\centering
\caption{Intraspecific correlations between total reproductive investment and (a) propagule investment and (b) flower investment, where flower investment is defined as 'flower weight $\times$ bud count'. Due to the high proportion of aborted flowers, flower investment was a better proxy of reproductive investment than was propagule investment. This was true both across species (Figure 3, Table 3 in the main text) and within species, as is shown here.}
\label{tab:propagule_invest_vs_repro}
\begin{tabular}{p{4cm}|x{.75cm}x{1cm}x{1.5cm}|x{.75cm}x{1cm}p{1.5cm}}
\hline
& \multicolumn{3}{c|}{Total reproductive investment} & \multicolumn{3}{c}{Total reproductive investment} \\
& \multicolumn{3}{c|}{vs. propagule investment} & \multicolumn{3}{c}{vs. flower investment} \\
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS17)
        , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

<<echo=FALSE, results='asis', warning=FALSE>>=
make_table_Table2_using_propagule <- function() {
slopes <- sma(repro_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
acc_by_species <- dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p)

slopes <- sma(accessory_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

slopes <- sma(success_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

slopes <- sma(pollen_attract_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

slopes <- sma(provisioning_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

slopes <- sma(discarded_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1,method="SMA", log="xy")
acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

slopes <- sma(prepollen_discarded_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
acc_by_species <- dplyr::bind_rows(acc_by_species,
  dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

slopes <- sma(postpollen_aborted_costs ~ propagule_costs,data=subset(SummarySpp[["mean"]]),slope.test=1, log="xy",method="SMA")
acc_by_species <- dplyr::bind_rows(acc_by_species, dplyr::select(slopes$groupsummary,r2,pval,Slope,Slope_lowCI,Slope_highCI,Int,Int_lowCI,Int_highCI,Slope_test_p))

acc_by_species$variable = c("total reproductive","total accessory","seed","pollen attraction","provisioning", "failed tissue","failed pre-pollination","failed provisioning")

acc_by_species$Slope <- format_r2(acc_by_species$Slope)
acc_by_species$Slope_lowCI <- format_r2(acc_by_species$Slope_lowCI)
acc_by_species$Slope_highCI <- format_r2(acc_by_species$Slope_highCI)

acc_by_species$slope2 <- paste(acc_by_species$Slope," (",acc_by_species$Slope_lowCI," - ",acc_by_species$Slope_highCI,")",sep="")

acc_by_species$r2 <- format_r2(acc_by_species$r2)
acc_by_species$pval <- format_p(acc_by_species$pval)
acc_by_species$Slope_test_p <- format_p(acc_by_species$Slope_test_p)
acc_slopes <- dplyr::select(acc_by_species,variable,r2,slope2,Slope_test_p)
}
TableS19 <- make_table_Table2_using_propagule()
names(TableS19) <- c("Costs","r$^2$","Slope (95$\\%$ CI)","p (slope test)")
TableS19$Costs <- firstup(TableS19$Costs)

@
\begin{table}[H]
\centering
\caption{Scaling of reproductive tissue costs with total propagule size. In this manuscript all "seed size" calculations use embryo and endosperm size, not propagule size. Most previous research has used propagule size as a measure of "seed size" and noted isometric relationships between various tissue costs and "seed size". Using embryo and endosperm size, these relationship did not exist for this data set, but are present if "seed size" includes the entire propagule.}
\label{tab:repro_tissues_vs_prop_size}
\begin{tabular}{p{5cm}|x{.75cm}x{3.5cm}p{3cm}}
\hline
<<echo=FALSE, results='asis', warning=FALSE>>=
print(xtable(TableS19)
         , sanitize.text.function=I
        , include.rownames = FALSE
        , include.colnames = TRUE,
        only.contents=TRUE)
@
\end{tabular}
\end{table}

@@

\subsection{Methods for calculating investment in reproductive tissues}

We collected data for 14 species (Table \ref{tab:species}) at 7 sites (Tables \ref{tab:sites}). Individuals were selected as described in the main text.

<<echo=FALSE,results='asis'>>=
  data <-  read.csv("../../data/species.csv", stringsAsFactors=FALSE, check.names=FALSE)
  data$Common_name <- firstup(data$Common_name)
  names(data) <-  clean_headers(names(data))

  print(xtable(data,
            align= 'p{1cm}p{5cm}p{3cm}p{3cm}p{2cm}p{3cm}',
            hline.after=c(1),
            label= "tab:species",
            caption="Details on study species."),
      , table.placement = "h"
      , caption.placement = "top"
      , include.rownames = FALSE
      , include.colnames = TRUE
      , size = "small"
      , tabular.environment = 'longtable'
      , floating = FALSE)

@@

  print(xtable(data,
            align= 'p{0.1cm}p{2cm}p{1cm}p{1cm}p{1cm}p{1.4cm}p{1.4cm}p{7cm}',
            hline.after=c(1),
            label= "tab:sites",
            caption="Details on study sites."),
      , table.placement = "h"
      , caption.placement = "top"
      , include.rownames = FALSE
      , include.colnames = TRUE
      , size = "small"
      , tabular.environment = 'longtable'
      , floating = FALSE)
@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

@@

Defines functions that estimate growth rates of the plant (not used in this analysis).

>>>>

\title{Investment in reproduction by 14 iteroparous perennials and its coordination with other life-history and functional traits}
\runninghead{I\lowercase{nvestment in reproduction}}

\author{E. H. Wenk\textsuperscript{1,\textasteriskcentered}, K. Abramowicz\textsuperscript{2}, M. Westoby\textsuperscript{1}, D.S. Falster\textsuperscript{3} }
\affiliation{
\textsuperscript{1} Biological Sciences, Macquarie University NSW 2109, Australia \\
\textsuperscript{2} Department of Mathematics and Mathematical Statistics, Ume{\aa} University, 90187 Ume{\aa}, Sweden \\
\textsuperscript{3} Evolution and Ecology Research Centre, University of New South Wales, Sydney NSW 2052, Australia \\
\textsuperscript{\textasteriskcentered} Correspondence author. E-mail: \email{ehwenk@gmail.com}
}

@@

flowering_parts <- read.csv("../Accessory/Sup_Table_flowering_parts.csv", stringsAsFactors=FALSE, check.names=FALSE)
flowering_parts$Method <- clean_headers(flowering_parts$Method)
flowering_parts$Part <- firstup(flowering_parts$Part)
flowering_parts$Description <- firstup(flowering_parts$Description)

@

@@

\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{figures/height.pdf}
\caption{Plots of plant height against estimated site age for the 14 study species. Species are sorted from top to bottom based on their Age at maturation (Table 1). The points indicate data points for the individual plants assessed, with colours indicating site age. Fitted lines are generalised additive models, with r$^2$ value indicating the amount of variance explained.}
\label{fig:height}
\end{figure}
\clearpage

\begin{figure}[h]
\centering
\includegraphics[height=20cm]{figures/RA_demo_all.pdf}
\caption{As in Fig. 3 but showing data for all 14 study species.}
\label{fig:RA_all}
\end{figure}
\clearpage

\begin{figure}[h]
\centering
\includegraphics[width=0.75\linewidth]{figures/leaf_loss.pdf}
\caption{Relationship between a species leaf mass per area and it's rate of annual leaf turnover.}
\label{fig:leaf_loss}
\end{figure}
\clearpage

@@

\subsection{Species and sites}

We collected data for 14 species (Table \ref{tab:species}) at 7 sites (Tables \ref{tab:sites}, Fig. \ref{fig:map}). Individuals were selected as described in the main text.

<<echo=FALSE,results='asis'>>=

data <-  read.csv("../../data/species.csv", stringsAsFactors=FALSE, check.names=FALSE)
data$Common_name <- firstup(data$Common_name)
i <- data$Previous_names != ""
data$Species_name[i] <- sprintf("%s (previously %s)", data$Species_name[i],data$Previous_names[i])
data <- dplyr::select(data,-Previous_names)

names(data) <-  clean_headers(names(data))

print(xtable(data,
          align= 'p{1cm}p{5cm}p{3cm}p{5cm}p{2cm}',
          hline.after=c(1),
          label= "tab:species",
          caption="Details on study species."),
    , table.placement = "h"
    , caption.placement = "top"
    , include.rownames = FALSE
    , include.colnames = TRUE
    , size = "small"
    , tabular.environment = 'longtable'
    , floating = FALSE)

@@

print(xtable(data,
          align= 'p{0.1cm}p{2cm}p{1cm}p{1cm}p{1cm}p{1.2cm}p{1.2cm}p{1.2cm}p{1.2cm}p{5cm}',
          hline.after=c(1),
          digits=c(0,0,0,2,0,0,0,4,4,0),
          label= "tab:sites",
          caption="Details on study sites."),
    , table.placement = "h"
    , caption.placement = "top"
    , include.rownames = FALSE
    , include.colnames = TRUE
    , size = "small"
    , tabular.environment = 'longtable'
    , floating = FALSE)
@

\begin{figure}[h]
\centering
\includegraphics[height=10cm]{../map.pdf}
\caption{Map of study locations.}
\label{fig:map}
\end{figure}

\clearpage
\subsection{Methods for calculating investment in reproductive tissues and growth}

@@

\subsubsection{Estimating leaf and stem growth}

XXXXX

@@

Also shown below  in Figs. \ref{fig:growth_Banksia_ericifolia}, \ref{fig:growth_Boronia_ledifolia},...., \ref{fig:growth_Pultenaea_tuberculata} are the relationships used to estimate growth in leaf and stem mass for each species.

@@

Fig. \ref{fig:growth_Banksia_ericifolia} shows the relationships used to estimate growth in leaf and stem mass for this species.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.6\linewidth]{../growth_plots/BAER.pdf}
\caption{Estimating growth in leaf and stem mass for \emph{Banksia ericifolia}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
estimated growth trajectory for each individual across an entire year.}
\label{fig:growth_Banksia_ericifolia}
\end{figure}

@@

Fig. \ref{fig:growth_Boronia_ledifolia} shows the relationships used to estimate growth in leaf and stem mass for this species.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.6\linewidth]{../growth_plots/BOLE.pdf}
\caption{Estimating growth in leaf and stem mass for \emph{Boronia ledifolia}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
estimated growth trajectory for each individual across an entire year.}
\label{fig:growth_Boronia_ledifolia}
\end{figure}

@@

Fig. \ref{fig:growth_Conospermum_ericifolium} shows the relationships used to estimate growth in leaf and stem mass for this species.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.6\linewidth]{../growth_plots/COER.pdf}
\caption{Estimating growth in leaf and stem mass for \emph{Conospermum ericifolium}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
estimated growth trajectory for each individual across an entire year.}
\label{fig:growth_Conospermum_ericifolium}
\end{figure}

@@

Fig. \ref{fig:growth_Epacris_microphylla} shows the relationships used to estimate growth in leaf and stem mass for this species.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.6\linewidth]{../growth_plots/EPMI.pdf}
\caption{Estimating growth in leaf and stem mass for \emph{Epacris microphylla}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
estimated growth trajectory for each individual across an entire year.}
\label{fig:growth_Epacris_microphylla}
\end{figure}
\clearpage

@@

Fig. \ref{fig:growth_Grevillea_buxifolia} shows the relationships used to estimate growth in leaf and stem mass for this species.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.6\linewidth]{../growth_plots/GRBU.pdf}
\caption{Estimating growth in leaf and stem mass for \emph{Grevillea buxifolia}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
estimated growth trajectory for each individual across an entire year.}
\label{fig:growth_Grevillea_buxifolia}
\end{figure}

@@

Fig. \ref{fig:growth_Grevillea_speciosa} shows the relationships used to estimate growth in leaf and stem mass for this species.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.6\linewidth]{../growth_plots/GRSP.pdf}
\caption{Estimating growth in leaf and stem mass for \emph{Grevillea speciosa}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
estimated growth trajectory for each individual across an entire year.}
\label{fig:growth_Grevillea_speciosa}
\end{figure}
\clearpage

@@

Fig. \ref{fig:growth_Hakea_teretifolia} shows the relationships used to estimate growth in leaf and stem mass for this species.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.6\linewidth]{../growth_plots/HATE.pdf}
\caption{Estimating growth in leaf and stem mass for \emph{Hakea teretifolia}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
estimated growth trajectory for each individual across an entire year.}
\label{fig:growth_Hakea_teretifolia}
\end{figure}
\clearpage

@@

Fig. \ref{fig:growth_Hemigenia_purpurea} shows the relationships used to estimate growth in leaf and stem mass for this species.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.6\linewidth]{../growth_plots/HEPU.pdf}
\caption{Estimating growth in leaf and stem mass for \emph{Hemigenia purpurea}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
estimated growth trajectory for each individual across an entire year.}
\label{fig:growth_Hemigenia_purpurea}
\end{figure}
\clearpage

@@

Fig. \ref{fig:growth_Leucopogon_esquamatus} shows the relationships used to estimate growth in leaf and stem mass for this species.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.6\linewidth]{../growth_plots/LEES.pdf}
\caption{Estimating growth in leaf and stem mass for \emph{Leucopogon esquamatus}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
estimated growth trajectory for each individual across an entire year.}
\label{fig:growth_Leucopogon_esquamatus}
\end{figure}
\clearpage

@@

Fig. \ref{fig:growth_Persoonia_lanceolata} shows the relationships used to estimate growth in leaf and stem mass for this species.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.6\linewidth]{../growth_plots/PELA.pdf}
\caption{Estimating growth in leaf and stem mass for \emph{Persoonia lanceolata}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
estimated growth trajectory for each individual across an entire year.}
\label{fig:growth_Persoonia_lanceolata}
\end{figure}
\clearpage

@@

Fig. \ref{fig:growth_Petrophile_pulchella} shows the relationships used to estimate growth in leaf and stem mass for this species.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.6\linewidth]{../growth_plots/PEPU.pdf}
\caption{Estimating growth in leaf and stem mass for \emph{Petrophile pulchella}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
estimated growth trajectory for each individual across an entire year.}
\label{fig:growth_Petrophile_pulchella}
\end{figure}
\clearpage

@@

Fig. \ref{fig:growth_Phyllota_phylicoides} shows the relationships used to estimate growth in leaf and stem mass for this species.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.6\linewidth]{../growth_plots/PHPH.pdf}
\caption{Estimating growth in leaf and stem mass for \emph{Phyllota phylicoides}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
estimated growth trajectory for each individual across an entire year.}
\label{fig:growth_Phyllota_phylicoides}
\end{figure}
\clearpage

@@

Fig. \ref{fig:growth_Pimelea_linifolia} shows the relationships used to estimate growth in leaf and stem mass for this species.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.6\linewidth]{../growth_plots/PILI.pdf}
\caption{Estimating growth in leaf and stem mass for \emph{Pimelea linifolia}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
estimated growth trajectory for each individual across an entire year.}
\label{fig:growth_Pimelea_linifolia}
\end{figure}
\clearpage

@@

Fig. \ref{fig:growth_Pultenaea_tuberculata} shows the relationships used to estimate growth in leaf and stem mass for this species.

@@

\begin{figure}[h]
\centering
\includegraphics[width=0.6\linewidth]{../growth_plots/PUTU.pdf}
\caption{Estimating growth in leaf and stem mass for \emph{Pultenaea tuberculata}. Colours indicate different site ages, as described in Fig. \ref{fig:height}. Red lines show the 
estimated growth trajectory for each individual across an entire year.}
\label{fig:growth_Pultenaea_tuberculata}
\end{figure}
\clearpage

@@

Defines functions that estimate growth rates of the plant.
